How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-07 tse-paper/content.tex
remove addressed todo
closes #43 Programming by Example, travis include pacage for algorithm

To fill this gap, we created three novel, prototypical
implementations to
automatically analyze build logs (step \circlenum{2}).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques by retrieving a substring (chunk) from the build log:
\begin{itemize}
	\item \emph{Program Synthesis by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

\begin{table*}[htb]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name & Acronym & Identification Technique & Granularity &
Configuration \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:techniques}
\end{table*}

@@

Techniques based on custom parsers (\#1
in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
since their creation is manual and one parser would never generalize
to the wide variety of build logs we are interested in.
The closest
we could come to the second most popular entry, regular expression, is
a technique to automatically derive them: in particular, we implement
a technique based on
\emph{Program Synthesis by Example (PBE)}.
It uses regular expressions internally, while simplifying their
development.

@@

\subsection{Program Synthesis by Example (PBE)}
The idea behind \emph{Programming by Example} is to automatically
generate a program, by capturing the
intent of the user through examples that the user provides.
Leveraging this approach, we designed a chunk retrieval technique
for build logs.
The \emph{PROSE library}~\cite{prose2019webpage} forms the basis for
our implementation.
This library builds on the generic program synthesis framework
\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
% Both enable \emph{PROSE} to synthesize regular expression programs
% consistent~\cite{mitchell1982generalization} with a set of in-
% and output examples.
% The usage of example enables the user to configure a chunk
% retrieval without understanding the whole structure of
% the build log.

@@

% TODO Caro: Not 100% sure about the 6 in the
% algorithm below.
% I had a set of rlogs before
% that, but then I think you only always retrieve 1 build
% log.
% However, I also looked into the LogChunks data set and saw more
% than 6 logs per project sometimes ...

% TODO: In addition, if there
% are more than 6 logs per project, aren't we missing another
% indirection in the algorithm?

@@

\subsubsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{High-level results of chunk retrieval with
		Program Synthesis by Example (PBE).}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall, and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with Program Synthesis by Example
(PBE).}
\end{figure*}

@@

\Cref{fig:failure-reason-categorycount-PBE} shows how
the results of PBE
runs depend on the number of structural categories in the training and
test examples.
% It shows the categories from above change depending on how many
% structural categories are present.
The figure demonstrates that program synthesis mostly
returns exactly the desired output when there is only one
structural category present in the training and test examples.
However, when
two or more structural categories are simultaneously present,
PROSE could in most cases not synthesize a program.
For four or more present
categories PROSE could never synthesize a consistent program.

@@

\subsubsection{Program Synthesis by Example (PBE)}

>>>>

To fill this gap, we created three novel, prototypical
implementations to
automatically analyze build logs (step \circlenum{2}).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques by retrieving a substring (chunk) from the build log:
\begin{itemize}
	\item \emph{Programming by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

\begin{table*}[htb]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name & Acronym & Identification Technique & Granularity &
Configuration \\
\midrule
Programming by Example & PBE	 & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:techniques}
\end{table*}

@@

Techniques based on custom parsers (\#1
in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
since their creation is manual and one parser would never generalize
to the wide variety of build logs we are interested in.
The closest
we could come to the second most popular entry, regular expression, is
a technique to automatically derive them: in particular, we implement
a technique based on
\emph{Programming by Example (PBE)}.
It uses regular expressions internally, while simplifying their
development.

@@

\subsection{Programming by Example (PBE)}
The idea behind \emph{Programming by Example} is to automatically
generate a program, by capturing the
intent of the user through examples that the user provides.
Leveraging this approach, we designed a chunk retrieval technique
for build logs.
The \emph{PROSE library}~\cite{prose2019webpage} forms the basis for
our implementation.
This library builds on the generic program synthesis framework
\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
% Both enable \emph{PROSE} to synthesize regular expression programs
% consistent~\cite{mitchell1982generalization} with a set of in-
% and output examples.
% The usage of example enables the user to configure a chunk
% retrieval without understanding the whole structure of
% the build log.

@@

@@

\subsubsection{Programming by Example (PBE)}
\label{sec:r:pbe}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{High-level results of chunk retrieval with
		Programming by Example (PBE).}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\begin{figure*}
\centering
    \textbf{Programming by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall, and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with Programming by Example
(PBE).}
\end{figure*}

@@

\Cref{fig:failure-reason-categorycount-PBE} shows how
the results of PBE
runs depend on the number of structural categories in the training and
test examples.
% It shows the categories from above change depending on how many
% structural categories are present.
The figure demonstrates that programming by example mostly
returns exactly the desired output when there is only one
structural category present in the training and test examples.
However, when
two or more structural categories are simultaneously present,
PROSE could in most cases not synthesize a program.
For four or more present
categories PROSE could never synthesize a consistent program.

@@

\subsubsection{Programming by Example (PBE)}
